%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Joshua Berger} \\ \vspace{1pt}
    Jacksonville, Florida 32246 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 904-429-2964 ~ \href{mailto:berger.joshua@outlook.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{berger.joshua@outlook.com}} ~ 
    \href{https://linkedin.com/in/joshberger5/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/joshberger5}}  ~
    \href{https://github.com/joshberger5/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/joshberger5}}
    \vspace{-8pt}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Backend software engineer with experience building scalable enterprise systems using Java, Spring Boot, and Kafka. Delivered production systems involving event-driven processing, multi-tenant architectures, and performance optimization. Known for shipping high-impact automation that reduced developer workload and improved system performance.
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Intercontinental Exchange}{August 2024 -- Present}
      {Software Engineer}{Jacksonville, Florida}
      \resumeItemListStart
        \resumeItem{Led complete rewrite of a business-critical Spring Boot microservice, migrating persistence from a tightly coupled third-party task engine to an internally developed data service to remove architectural constraints and improve long-term extensibility.}

        \resumeItem{Designed and implemented event-driven bulk processing using Kafka, publishing one event per entity and leveraging asynchronous consumers to enable scalable, non-blocking mass operations.}

        \resumeItem{Implemented audit-tracked persistence models and Specification-based dynamic querying with JWT-enforced organization-scoped multi-tenancy.}

        \resumeItem{Engineered an automated metadata generation system eliminating manual configuration for 30,000+ UI fields across 1,100 legacy application screens.}

        \resumeItem{Parsed and analyzed 2,000 legacy HTML artifacts to reverse-engineer undocumented business rules and standardize metadata generation.}

        \resumeItem{Developed a backend API endpoint that generated standardized metadata on-demand via an internal LLM service, reducing per-screen configuration time by 30–45 minutes and enabling 50 developers to complete all remaining submissions in a single day.}

        \resumeItem{Reduced API latency by 10+ seconds through query optimization and improved data access patterns.}

        \resumeItem{Increased mutation test coverage by 20\% using PIT by refactoring legacy tests and strengthening regression safety for critical workflows.}

    \resumeItemListEnd

    \resumeSubheading
      {Intercontinental Exchange}{May -- August 2024}
      {Software Engineer Intern}{Jacksonville, Florida}
      \resumeItemListStart
        \resumeItem{Selected as 1 of 3 interns (out of 50+) to receive a return offer after leading a 6-person intern team to deliver a production-ready backend service integrated with legacy mainframe systems.}
    \resumeItemListEnd

    \resumeSubheading
      {Furman University}{August -- December 2023}
      {Teaching Assistant}{Greenville, South Carolina}
      \resumeItemListStart
        \resumeItem{Assisted 30+ students with programming fundamentals and debugging support, reinforcing core software design and problem-solving concepts.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, SQL, C\#} \\
     \textbf{Backend \& Architecture}{: Spring Boot, Kafka, REST APIs, OpenAPI, PostgreSQL, Liquibase, JWT-based Auth} \\
     \textbf{Testing \& Tooling}{: JUnit, PIT Mutation Testing, Git} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Automated Job Discovery \& Notification System} $|$ \emph{Python, GitHub Actions, REST APIs}}{February 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Architected a layered job aggregation system using Domain-Driven Design, integrating concurrent REST API clients across 10+ job boards (Adzuna, Greenhouse, Lever, Workday) with deduplication and salary normalization.}
            \resumeItem{Integrated an LLM-based title filtering layer (Gemini) behind a deterministic keyword filter to reduce false-positive alerts while minimizing API cost and latency.}
            \resumeItem{Deployed as a fully automated GitHub Actions pipeline running 3$\times$ daily with HTML email delivery and persistent state tracking across runs.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Furman University}{}
        {Bachelor of Science in Computer Science}{Greenville, South Carolina}
        \resumeItemListStart
          \resumeItem{Heatherington Scholarship recipient for outstanding academic performance (3.93 CS GPA).}
          \resumeItem{Member, Upsilon Pi Epsilon (Computing Honor Society).}
        \resumeItemListEnd
      \resumeSubHeadingListEnd

\end{document}
